ggalluvial: Layered Grammar for Alluvial Plots

### 2020-12-01 README.rmd
pkg: doc formatting + version/date + debug citation + revdep lists

- **alluvial** understands a variety of inputs (vectors, lists, data frames), whereas **ggalluvial** requires a single data frame;
- **alluvial** uses each variable of these inputs as a dimension of the data, whereas **ggalluvial** requires the user to specify the dimensions, either as separate aesthetics or as [key-value pairs](https://tidyr.tidyverse.org/);
- **alluvial** produces both the *alluvia*, which link cohorts across multiple dimensions, and (what are here called) the *strata*, which partition the data along each dimension, in a single function; whereas **ggalluvial** relies on separate layers (stats and geoms) to produce strata, alluvia, and alluvial segments called *lodes* and *flows*.

>>>>

- **alluvial** understands a variety of inputs (vectors, lists, data frames), whereas **ggalluvial** requires a single data frame;
- **alluvial** uses each variable of these inputs as a dimension of the data, whereas **ggalluvial** requires the user to specify the dimensions, either as separate aesthetics or as [key-value pairs](https://tidyr.tidyverse.org/);
- **alluvial** produces both the _alluvia_, which link cohorts across multiple dimensions, and (what are here called) the _strata_, which partition the data along each dimension, in a single function; whereas **ggalluvial** relies on separate layers (stats and geoms) to produce strata, alluvia, and alluvial segments called _lodes_ and _flows_.
